---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
```{r Loaddata, echo = TRUE}
origdata <- read.csv("activity.csv")
head(origdata)
## Observation: No processing/tranforming data required at this point.
```



## Question: What is mean total number of steps taken per day?
**Note we can ignore na values for this question**
1. Make a histogram of the total number of steps taken each day
2. Calculate and report the **mean** and **median** total number of steps taken per day
```{r meanmedian, echo = TRUE}
daily_sum <- tapply(X = origdata$steps, INDEX = origdata$date,  FUN = sum, na.rm = TRUE)
median(daily_sum)
mean(daily_sum)

hist(daily_sum, xlab = "Total steps taken daily", main = "Daily steps taken", 
     col = c("red", "blue", "green", "purple", "orange"), breaks = 10)
```

## What is the average daily activity pattern?
1. Make a time series plot (i.e. `type = "l"`) of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)
2. Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?
```{r averagedailyactivity, echo = TRUE}
daily_average <- tapply(X = origdata$steps, INDEX = origdata$interval,  FUN = mean, na.rm = TRUE)
plot(names(daily_average), daily_average, type = "l", xlab = "5 minute intervals", ylab = "Average daily steps", col = "red", main = " Daily activity")

max_interval <- names(which.max(daily_average))
max_steps <- max(daily_average)

print(paste("At interval", max_interval, "the max daily average for this trial period is", max_steps))
```



## Imputing missing values
```{r Impute missing data, echo= TRUE}

```



## Are there differences in activity patterns between weekdays and weekends?
